Scottish Child Payment Interventions

### 2024-01-19 minos/outcomes/SCP_vis.Rmd
Stopped producing plot for disabled priority subgroup as the filter is killing the script. Needs some work, just turning off for now as rest of script is good.

```{r}
#out.path <- here::here('output', 'default_config')
#out.path <- here::here('output', 'glasgow_scaled')
out.path <- here::here('output', 'scaled_scotland')

@@

SF12.change.priority.group(int.list, scen.list, priority.group = 'minority_ethnic')
SF12.change.priority.group(int.list, scen.list, priority.group = 'child_under_one')
SF12.change.priority.group(int.list, scen.list, priority.group = 'three_plus_children')
SF12.change.priority.group(int.list, scen.list, priority.group = 'mother_under_25')
SF12.change.priority.group(int.list, scen.list, priority.group = 'disabled')

>>>>

```{r}
#out.path <- here::here('output', 'default_config')
out.path <- here::here('output', 'glasgow_scaled')
#out.path <- here::here('output', 'scaled_scotland')

@@

SF12.change.priority.group(int.list, scen.list, priority.group = 'minority_ethnic')
SF12.change.priority.group(int.list, scen.list, priority.group = 'child_under_one')
SF12.change.priority.group(int.list, scen.list, priority.group = 'three_plus_children')
SF12.change.priority.group(int.list, scen.list, priority.group = 'mother_under_25')
#SF12.change.priority.group(int.list, scen.list, priority.group = 'disabled')
